Radio Emission from Red-Giant Hot Jupiters

### 2015-09-21 ms.tex
photon -> electron

For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and the mean free path of the electrons is $\sim 2R_J$. 
In practice, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we consider the cascade where an electron with energy $E _{\rm in}$ ionize an atom releasing two electrons  (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each. 
Note that the proton will not acquire much energy due to the conservation of momentum and conservation of energy. \memoYF{in more detail?}
For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce a photon with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum. 
In reality, not all released electrons may be able to proceed the next ionization. Letting $\xi $ represent the fraction of released electrons that proceed to the next ionization, the number of ionized atoms through this cascade, $\alpha $, is
%%%%%%%%%
\begin{equation}
\alpha = (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3. 
\end{equation}
%%%%%%%%%
With $\xi = 0.8 $, this gives $\alpha \sim 5$. 
Then, $\dot{N}_X $ in equation (\ref{eq:equilibrium}) is replaced by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \alpha \dot{N}_X. 
\end{equation}
%%%%%%%%%

>>>>

For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and the mean free path of the electrons is $\sim 2R_J$. 
In practice, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we consider the cascade where an electron with energy $E _{\rm in}$ ionize an atom releasing two electrons  (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each. 
Note that the proton will not acquire much energy due to the conservation of momentum and conservation of energy. \memoYF{in more detail?}
For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce an electron with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum. 
In reality, not all released electrons may be able to proceed the next ionization. Letting $\xi $ represent the fraction of released electrons that proceed to the next ionization, the number of ionized atoms through this cascade, $\alpha $, is
%%%%%%%%%
\begin{equation}
\alpha = (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3. 
\end{equation}
%%%%%%%%%
With $\xi = 0.8 $, this gives $\alpha \sim 5$. 
Then, $\dot{N}_X $ in equation (\ref{eq:equilibrium}) is replaced by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \alpha \dot{N}_X. 
\end{equation}
%%%%%%%%%
